Notes on conformal manifolds

### 2025-07-28 Draft_MLFlatDirections.tex
Upadte of sec. 5, and small modifications in sec. 4.4.

	The supergravity solution can be shown to preserve a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry. Using the parametrisation~\eqref{eq:rulex8x10}, the $(x_{1},x_{2},x_{4})$ moduli space is most nicely parametrised using the change of coordinates
	\begin{equation}
		x_{1} = r\cos(\theta)\cos(\Phi), \quad x_{2} = r\cos(\theta)\sin(\Phi) \quad {\rm and} \quad x_{4} = r\sin(\theta),
	\end{equation}
	for which the Zamolodchikov metric reads
	\begin{equation}
		\d^{2}s_{\rm Zam.} = -\,\d r^{2} - r^{2}\,\bigg(\d \theta^{2} - r\cos(\theta)\,\d \theta\d\Phi + \sin(\theta)\,\d r\d\Phi + \frac{1}{2}\,\big(3+r^{2}-\cos(2\theta)\big)\,\d\Phi^{2} \bigg).
	\end{equation}

\section{Conclusion} \label{sec:ccl}
We have presented a novel machine learning approach to systematically identify and characterise flat directions in supergravity scalar potentials. Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression on polynomials. We demonstrated its efficiency on a 5-scalar subsector of three-dimensional half-maximal supergravity, derived from the $AdS_3 \times S^3 \times T^4$ compactification of IIB supergravity.

@@

Our analysis reveals that the 5-dimensional scalar space contains a 3-dimensional conformal manifold, with one direction potentially gauge-fixable. The discovered solution preserves $U(1) \times U(1)$ gauged symmetry and exhibits a rich spectrum structure. The Zamolodchikov metric on the moduli space, parametrized by spherical-like coordinates, provides a concrete geometric description of the conformal manifold. \ce{This paragraph has to change given the few information we give on the sugra solution. Also, conformal manifold not defined. Rather open on the fact that having the analytical definition of the family gives access to its study using sugra and ExFT?}

@@

@@

While the specific solution found in this 5-scalar model may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit. \ce{Move above when discussing the sugra solution?}

\ce{Open on the use of ExFT to uplift and compute the full KK spectrum.}

>>>>

	The supergravity solution can be shown to preserve a ${\rm U}(1)\times{\rm U}(1)$ gauged symmetry and breaks all supersymmetry, except at the origin where we recover the ${\rm SO}(4)$ isometries and the ${\cal N}=(0,4)$ supercharges. Using the parametrisation~\eqref{eq:rulex8x10}, the $(x_{1},x_{2},x_{4})$ moduli space is most nicely parametrised using the change of coordinates
	\begin{equation}
		x_{1} = r\cos(\theta)\cos(\Phi), \quad x_{2} = r\cos(\theta)\sin(\Phi) \quad {\rm and} \quad x_{4} = r\sin(\theta),
	\end{equation}
	for which the Zamolodchikov metric reads
	\begin{equation}
		\d^{2}s_{\rm Zam.} = -\,\d r^{2} - r^{2}\,\bigg(\d \theta^{2} - r\cos(\theta)\,\d \theta\d\Phi + \sin(\theta)\,\d r\d\Phi + \frac{1}{2}\,\big(3+r^{2}-\cos(2\theta)\big)\,\d\Phi^{2} \bigg).
	\end{equation}

	\ce{Wouldn't it be interesting to give the scalar masses and speak of the stability of the 3d solution? Would be useful to make contact with ref.~\cite{Eloy:2021fhc}.}

\section{Conclusion} \label{sec:ccl}
We have presented a novel machine learning approach to systematically identify and characterise flat directions in supergravity scalar potentials. Our methodology combines gradient descent sampling with annealed importance sampling for symbolic regression on polynomials. We demonstrated its efficiency on a 5-scalar subsector of three-dimensional half-maximal supergravity, derived from the ${\rm AdS}_3 \times S^3$ compactification of six-dimensional ${\cal N}=(1,1)$ supergravity, or analogously of the ${\rm AdS}_3 \times S^3 \times T^4$ compactification of IIB supergravity.

@@

@@

Our analysis reveals that the 5-dimensional scalar space contains a 3-dimensional conformal manifold. The discovered solutions preserve a ${\rm U}(1) \times {\rm U}(1)$ gauged symmetry and breaks all supersymmetries. The Zamolodchikov metric on the moduli space provides a concrete geometric description of the conformal manifold. While the specific solutions found may have limited direct physical applications, the demonstrated feasibility of our approach and its potential for systematic classification of flat directions across the supergravity landscape make it a valuable addition to the theoretical physicist's toolkit. As the solutions live in a 3d consistent truncation of both the ${\rm AdS}_3 \times S^3$ solution of ${\cal N}=(1,1)$ six-dimensional supergravity and of the ${\rm AdS}_3 \times S^3 \times T^4$ vacuum of IIB supergravity, we can uplift the solution to 6d and 10d using the tools of exceptional field theory (ExFT)~\cite{Hohm:2014fxa,Hohm:2014qga,Hohm:2017wtr}. The higher-dimensional solutions would be of the form ${\rm AdS}_3 \times M^3$ or ${\rm AdS}_3 \times M^7$, with $M^{3}$, and $M^{7}$ being deformations of the round $S^{3}$ and $S^{3}\times {\rm T}^{4}$, respectively. These deformed spaces have as moduli the 3 parameters $\{x_{1},x_{2},x_{4}\}$ that define the solutions. ExFT gives further access to the full Kaluza-Klein spectrum for those compactifications~\cite{Malek:2019eaz,Malek:2020yue,Eloy:2020uix}, allowing a test of the perturbative stability of the solutions, and giving valuable information on the spectrum of states of the dual CFT. These applications relies entirely on the fact that we have an analytic parametrisation of the solutions thanks to the symbolic regression we performed. We live these for future works.

@@
